Ae. albopictus CPP manuscript

### 2020-04-13 Albopictus_cpp_MS.Rmd

#Spearman rank correlation coefficients
cor.test(filter(DI_short_2, country=="US", year==2018)$lat, filter(DI_short, country=="US", year==2018)$DI, alternative="two.sided", method="spearman")
cor.test(filter(DI_short_2, country=="JP", year==2018)$lat, filter(DI_short, country=="JP", year==2018)$DI, alternative="two.sided", method="spearman")

@@

#bw locations map
us_map_bw<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="black") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 2) + xlim(c(-87, -65)) + ylim(c(24,48)) +
  geom_label_repel(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), nudge_x=1.5, size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm")) + xlab("") + ylab("")

japan_map_bw<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="black") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 2)  + xlim(c(125, 147)) + ylim(c(24,48)) +
  geom_label_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm")) + xlab("") + ylab("Latitude")

>>>>

#Spearman rank correlation coefficients
cor.test(filter(DI_short, country=="US", year==2018)$lat, filter(DI_short, country=="US", year==2018)$DI, alternative="two.sided", method="spearman")
cor.test(filter(DI_short, country=="JP", year==2018)$lat, filter(DI_short, country=="JP", year==2018)$DI, alternative="two.sided", method="spearman")

@@

#bw locations map
us_map_bw<-ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") + 
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="US"), aes(x = longitude, y = latitude), size = 2, shape=21, color="black", fill="gray", stroke=1) + xlim(c(-87, -65)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="US"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), nudge_x=1.5, size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("")

japan_map_bw<-ggplot() + geom_polygon(data = jp, aes(x=long, y = lat, group=group), fill=NA, color="dark gray") +
  coord_fixed(1.3) + geom_point(data = filter(pops, country=="JP", only_2008=="n"), aes(x = longitude, y = latitude), size = 2)  + xlim(c(125, 147)) + ylim(c(24,48)) +
  geom_text_repel(data=filter(pops, country=="JP", only_2008=="n"), aes(x=longitude, y=latitude, label=pop), hjust=0, label.padding=unit(0.1, "lines"), size=4) + theme_bw() + theme(text=element_text(size=24), plot.margin = unit(c(0,0,0,0), "cm"), panel.grid=element_line(size=0.1)) + xlab("") + ylab("Latitude")
